Method to infer relatedness using low coverage ancient DNA

### 2021-12-13 paper_overleaf/main.tex

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/fil0_relatable_plot.png}
    \caption{Application of KIn on Neandertal specimens from Chagyrskaya}
    \label{fig5}
\end{figure}

@@

>>>>

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/fil0_relatable_plot.png}
    \caption{Application of KIn on Neandertal specimens from Chagyrskaya. Color of a square represents the relatedness, while the number denotes loglikelihood ratio.}
    \label{fig5}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/binom.png}
    \caption{Beta binomial distribution is a better fit compared to Binomial for proportion of difference in windows}
    \label{figS1}
\end{figure}
